---
title: "Data 607 Assignment 9"
author: "Jayden Jiang"
date: "2024-12-11"
output: html_document
---
## Library
```{r}
library(httr)
library(jsonlite)
library(dplyr)
library(tidyr)
```

## Introduction
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and
transform it into an R DataFrame.

Here I chose Book API, which provides information about book reviews and The New York Times best seller list. 

## Store API Key
```{r}
# Store the API Key securely
file.edit("~/.Renviron")
api_key <- Sys.getenv("nyt_api_key")
if (api_key == "") {
  stop("API Key not found.")
}
```

## Transform from JSON to R Dataframe 
```{r}

best_sellers <- paste0("https://api.nytimes.com/svc/books/v3/lists/full-overview.json?api-key=", api_key)

response <- GET(best_sellers)
if (http_status(response)$category != "Success") {
  stop("Failed to retrive data.")
}

books_content<- content(response, as = "text", encoding = "UTF-8")

books_data <- fromJSON(books_content)

books_df <- books_data$results$lists %>%
  unnest(col = c(books)) %>%
  as.data.frame()

glimpse(books_df)
```
## Clean and Tidy Data For Top 10 Fiction & Non-Fiction
```{r}
# Clean data
clean_books_df <- books_df %>%
  select(list_name, title, author, rank, rank_last_week, weeks_on_list, description, publisher, book_image, buy_links)
head(clean_books_df)
```


```{r}
# Find Top-Ranked Fictions
top_10_fiction <- clean_books_df %>%
  filter(list_name == "Combined Print and E-Book Fiction") %>%
  arrange(rank) %>%
  slice_head(n = 10) %>%
  select(rank, list_name, title)
top_10_fiction
```
```{r}
#Find Top-Ranked Non-Fictions
top_10_nonfiction <- clean_books_df %>%
  filter(list_name == "Combined Print and E-Book Nonfiction") %>%
  arrange(rank) %>%
  slice_head(n = 10) %>%
  select(rank, list_name, title)
top_10_nonfiction
```
## Conclusion 
For this assignment, we aiming to transform JSON format data from The New York Time API into R data frame. As well as to have ability to continuously working with the data. 



